Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
reverses section split

### Editing SR
```{r SR edit}
SR <- lapply(
  X   = SR,
  FUN = edit_rules
  )
```

@@

# Remove objects
rm(
  SR, sequences,
  my_cspade, my_ruleInduction, clean_rules, compute_rhs.support, edit_rules, make_SR,
  n_students
)
```

>>>>

### Editing SR
We apply `edit_rules` to SR in order to get easily readable rules. 
```{r SR edit}
SR <- lapply(
  X   = SR,
  FUN = edit_rules
  )
```

@@

#
# Remove objects
rm(
  SR, sequences,
  my_cspade, my_ruleInduction, clean_rules, compute_rhs.support, edit_rules, make_SR,
  n_students
)
```
